---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# openCPUPrac

<!-- badges: start -->
<!-- badges: end -->

The goal of openCPUPrac is to ...

## Installation

You can install the development version of openCPUPrac like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(openCPUPrac)
## basic example code
```

# Questions to ask 

  1. Add data to existing call.
  2. Add/remove button on site.
  3. Revert change on site.
  4. Create new data model/API access point.
  5. Create a new page. 
  
    
# Data server

  1. Where is is stored?
  2. How do we update?
  3. How is is backed-up?
  4. Sources to learn more. 
  5. How do we move?
  6. How do we start from scratch? 

# JS server  

  1. Where is is stored?
  2. How do we update?
  3. How is is backed-up?
  4. Sources to learn more. 
  5. How do we move?
  6. How do we start from scratch? 



